---
title: "Youtube Music Video Analysis"
author: "Christopher Luke"
date: "2025-10-09"
output: html_document
---
Goal: Investigate data set containing information on the top 100 music videos on YouTube in 2025. This approach will utilize R to load, transform and visualize trends such as popularity rank while also observing potential relationships between channel follower count and video views. 

Libraries used: dplyr and ggplot2 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Loading csv file and transforming it into a dataframe 
```{r}
library(dplyr)
library(ggplot2)
path <- "C:/Users/chris/OneDrive/Desktop/youtube-top-100-songs-2025.csv"
tibble <- read.csv(path)
glimpse(tibble)
```

Transforming dataframe, including sorting by view count descending and creating a corresponding rank column, and calculating average viewer count per channel 
```{r}
tibble <- tibble %>% arrange(channel, desc(view_count))
tibble <- tibble %>% mutate(rank = rank(-view_count))
avgviewsperchannel <- tibble %>% group_by(channel) %>% summarise (avgviews = mean(view_count), count = n(), channel_follower_count = first(channel_follower_count))
head(avgviewsperchannel,10)
```

Visualizing results and fitting a linear regression model to understand potential relationships 
```{r}
scatter <- ggplot(avgviewsperchannel, aes(x = channel_follower_count, y = avgviews)) + geom_point()
print(scatter)
linearmodel <- lm(avgviews ~ channel_follower_count, data = avgviewsperchannel)
summary(linearmodel)
```

Results summary provides statistics regarding the linear model, showing a statistically insignificant relatinoship between a channel's follower count and its average video reviews 